\documentclass[11pt]{article}

% Use the following to compile
% mkdir tmp
% pdflatex -aux-directory=tmp -output-directory=tmp --shell-escape notes.tex

% Package use definitions
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{comment}
\usepackage[outputdir=tmp]{minted}
\usepackage[dvipsnames]{xcolor}
\usepackage{listings}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{tabu}
\usepackage{upgreek}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[nottoc]{tocbibind}
\usepackage{natbib}

\setlength{\parindent}{11pt}
\setlength{\parskip}{0pt}

% Header and footer setup
\pagestyle{fancy} \rhead{\today} \lhead{Reinforcement Learning conceptions for
  Poker} \renewcommand{\headrulewidth}{1pt} \renewcommand{\footrulewidth}{1pt}

% Image directory specification
\graphicspath{ {./images/} }

% Settings minted option for the entire document
\definecolor{LightGray}{rgb}{0.9, 0.9, 0.9}
\setminted{frame=lines,framesep=2mm,bgcolor=LightGray,linenos,
  fontsize=\footnotesize, baselinestretch=1.2}

% Start of document
\begin{document}

% Title page and table of contents setup
\begin{titlepage}
  \begin{center}
    \vspace*{1cm} \Huge \textbf{Bounding Eccentricities}\\
    \vspace*{1\baselineskip} Very Large Graphs\\
    \vspace*{2\baselineskip} \large
    \begin{abstract}
      \noindent
    %% This paper is a summary of our research and development of the Bounding
    %% Eccentricities algorithm introduced in the 2013 article Computing the
    %% Eccentricity Distribution of Large Graphs by Frank W. Takes and Walter
    %% A. Kosters. In this report we restate all of the methodologies from the
    %% original paper that were applied during the implementation of the Bounding
    %% Eccentricities algorithm, as well as any other external concepts originating
    %% from other research on the same topic. We also show the results of various
    %% experiments using the same performance measures as in the original paper for
    %% the sake of simplifying comparison. Additionally, we also show the relative
    %% improvement brought forth by of all of the main methodologies introduced in
    %% the paper over previous versions, namely selection strategies and graph
      %% prunning.
    Ce document est un résumé de nos recherches et du développement de
    l'algorithme Bounding Eccentricities introduit dans l'article de 2013
    Computing the Eccentricity Distribution of Large Graphs de Frank W. Takes et
    Walter A. Kosters. Dans ce rapport, nous reprenons toutes les méthodologies
    de l'article original qui ont été appliquées lors de I' implémentation de
    l'algorithme Bounding Eccentricities, ainsi que tout autre concept externe
    provenant d'autres recherches sur le même sujet. Nous montrons également les
    résultats de diverses expériences en utilisant les mêmes mesures de
    performance que dans l'article original afin de simplifier la
    comparaison. En outre, nous montrons l'amélioration relative apportée par
    toutes les principales méthodologies introduites dans l'article par rapport
    aux versions précédentes, à savoir les stratégies de sélection et
    l'optimisation des graphes.
    \end{abstract}
    \vfill \normalsize \textbf{Théo Minary : theo.minary@epita.fr}\\ \textbf{Jose
      A. Henriquez Roa : jose.henriquez-roa@epita.fr}\\
    \vspace*{2\baselineskip} \today \rhead{\today}
    \newpage
    \normalsize \tableofcontents
    \newpage
  \end{center}
\end{titlepage}
\section{Experiments}
%% In this section we present some performance analysis of our implementation of
%% this algorithm. To assess the performance of our implementation with respect to
%% the results found in section 6 of the paper [1] we provide some of the same
%% performance measures. We have thus measured the number of execution of our
%% shortest path search algorithm required to compute all of the eccentricities. In
%% this section we shall first analyse the performance of the different selection
%% strategies as well as the graph prunning strategy given in the paper. The number
%% of iteration taken after the implementation of each method presented in the
%% respective columns for the ca-CondMat, ca-HepPh and ca-HepTh is given in the
%% following table:
Dans cette section, nous présentons une analyse des performances de notre
implémentation de cet algorithme. Pour évaluer les performances de notre
implémentation par rapport aux résultats trouvés dans la section 6 de l'article
[1], nous fournissons certaines des mêmes mesures de performance. Nous avons
ainsi mesuré le nombre d'exécution de notre algorithme de recherche du plus
court chemin nécessaire pour calculer toutes les excentricités. Dans cette
section, nous allons d'abord analyser les performances des différentes
stratégies de sélection ainsi que la stratégie de prunning du graphe donnée dans
l'article. Le nombre d'itérations prises après l'implémentation de chaque
méthode présentée dans les colonnes respectives pour les ca-CondMat, ca-HepPh et
ca-HepTh est donné dans le tableau suivant :\\
\begin{center}
 \begin{tabular}{||c c c c c||} 
   \hline
   Dataset & Random & Pruning & Interchanging bound & Degree centrality \\
   \hline\hline
   ca-HepPh & 8444 & 8211 & 1662 & 1589 \\
   \hline
   ca-HepTh & 6175 & 5886 & 1101 & 1053 \\
   \hline
   ca-CondMat & 9439 & 9268 & 3486 & 3271 \\ 
   \hline
 \end{tabular}
\end{center}
\medskip
\noindent
The best performing variant was evaluated on 2 more datasets of higher
sizes. The following table shows the results:\\
\begin{center}
 \begin{tabular}{||c c c c c||} 
   \hline
   Dataset & Nodes & Edges & Pruned & Iterations \\
   \hline\hline
   ca-HepPh & 11\ 204 & 117\ 619 & 282 & 1\ 589 \\
   \hline
   ca-HepTh & 8\ 638 & 24\ 806 & 351 & 1\ 051 \\
   \hline
   ca-CondMat & 21\ 363 & 91\ 286 & 353 & 3\ 271 \\ 
   \hline
   web-NotreDame & 325\ 729 & 1\ 090\ 108 & 141\ 178 & 142 \\
   \hline
   web-Stanford & 255\ 265 & 1\ 941\ 926 & 1\ 0350 & 9 \\
   \hline
 \end{tabular}
\end{center}
\section{Conclusion}
%% We have thus implemented the algorithm and have found very similar results for
%% each of the graphs used in the paper. We also have seen the relative improvement
%% of each optimization method proposed in the paper. However, there are still some
%% improvements that can be performed. A possible route for improvement would be to
%% find a better candidate selection method, however this would require more
%% research to be performed. Another route for improvement that would require less
%% effort would be to parallelise the shortest path computations to leverage as
%% most as possible multiple core systems which are much more popular today than
%% they were in 2013.
Nous avons donc implémenté l'algorithme et avons trouvé des résultats très
similaires pour chacun des graphes utilisés dans l'article. Nous avons également
constaté l'amélioration relative de chaque méthode d'optimisation proposée dans
l'article. Cependant, certaines améliorations peuvent encore être réalisées. Une
voie d'amélioration possible serait de trouver une meilleure méthode de
sélection des candidats, mais cela nécessiterait plus de recherches. Une autre
voie d'amélioration qui demanderait moins d'efforts serait de paralléliser les
calculs du plus court chemin afin d'exploiter au maximum les systèmes à
plusieurs cœurs qui sont beaucoup plus populaires aujourd'hui qu'ils ne
l'étaient en 2013.
\section{References}
\begin{enumerate}
\item Takes, F.W.; Kosters, W.A. Computing the Eccentricity Distribution of Large Graphs. Algorithms 2013, 6, 100-118. https://doi.org/10.3390/a6010100
\item Frank W. Takes and Walter A. Kosters. 2011. Determining the diameter of small world networks. In Proceedings of the 20th ACM international conference on Information and knowledge management (CIKM '11). Association for Computing Machinery, New York, NY, USA, 1191–1196. DOI:https://doi.org/10.1145/2063576.2063748
\end{enumerate}
\end{document}
